---
title: "Dataset comparison"
author: "Dan Rozelle"
date: "July 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 2)
source("curation_scripts.R")
s3_cd("/ClinicalData/ProcessedData")
```

#### import data
We're comparing clinical data from three apparent datasets: 

- MGP integrated cohort with MMRF IA9 clinical data
- MGP integrated cohort with MMRF IA10 clinical data
- UAMS derived exome cohort with IA9 clinical data


```{r}
meta <- s3_get_table("JointData/curated.metadata.2017-07-07.txt")
inv  <- s3_get_table("Reports/counts.by.individual.2017-07-25.txt")

ia9  <- s3_get_table("Integrated/archive/unified.clinical.nd.tumor_IA9_2017-03-23.txt")
# filter to only include patients with WES results (not just WES files)
ia9.wes <- ia9 %>% filter( Patient %in% inv[inv$INV_Has.nd.snv == 1,"Patient"]) %>%
  mutate(set = "ia9")

ia9.qc  <- s3_get_with("/ClinicalData/OriginalData/MMRF_IA9",
                       "MMRF_CoMMpass_IA9_Seq_QC_Summary.xlsx",
                       FUN = auto_read) %>%
  select(QC.Link.SampleName, MMRF_Release_Status)%>%
  rename(File_Name = QC.Link.SampleName, IA9_Status = MMRF_Release_Status)

ia10 <- s3_get_table("ND_Tumor_MM/per.patient.unified.nd.tumor.2017-07-27.txt")
ia10.wes <- ia10 %>% filter( Patient %in% inv[inv$INV_Has.nd.snv == 1,"Patient"]) %>%
  mutate(set = "ia10")
ia10.qc <- s3_get_with("/ClinicalData/OriginalData/MMRF_IA10c/README_FILES",
                       "MMRF_CoMMpass_IA10_Seq_QC_Summary.xlsx",
                       FUN = auto_read) %>%
  select(QC.Link.SampleName, MMRF_Release_Status) %>%
  rename(File_Name = QC.Link.SampleName, IA10_Status = MMRF_Release_Status)

u1313 <- auto_read("~/Desktop/1313_samples.csv")%>%
  mutate(set = "u1313")
```

#### Comparison of total patient numbers
This includes all valid NDMM patients, but does not require any data types.  
```{r}
venn::venn(list(MGP_IA9  = ia9$Patient, 
                MGP_IA10 = ia10$Patient, 
                u1313    = u1313$Patient), 
           cexsn = 1, cexil = 1, zcolor = "style")
```


#### Comparison of total patient numbers for patients with exome seq
This is the direct comparison of patients from each dataset where we have valid 
exome seq results. 
```{r}
venn::venn(list(MGP_IA9_WES  = ia9.wes$Patient,
                MGP_IA10_WES = ia10.wes$Patient, 
                u1313    = u1313$Patient), 
           cexsn = 1, cexil = 1, zcolor = "style")

# 40 uniquely in u1313 dataset
# 
# 20 of these are  DFCI samples that were reclassified as Relapse
# 16 MMRF were classified as PCL
# 4 MMRF were replaced after QC issues, they have newer files in IA10 for future analysis
fourty <- u1313[!u1313$Patient %in% c(ia9.wes$Patient,ia10.wes$Patient),]
fourty$Patient

meta %>% filter(File_Name %in% fourty$File_Name) %>%
  select(Patient, File_Name, Disease_Status, Disease_Type, Excluded_Flag) %>%
  left_join(., ia10.qc, by = "File_Name") %>%
  select(-Patient) %>%
  DT::datatable(options = list(pageLength = 10, dom = 'tip'))


```

#### Clinical parameter comparison

```{r}
extract <- function(df){
  df %>% 
    select(set, Study, D_Gender, D_Age, D_OS, D_OS_FLAG, D_PFS, D_PFS_FLAG) %>%
    mutate(D_Gender = (D_Gender == "Male")) %>%
    rename(D_Gender_Male = D_Gender) %>%
    group_by(set, Study) %>%
    summarise_all(funs(mean = round(mean(., na.rm = T),2),
                       # sd   = sd(., na.rm = T),
                       n    = sum(!is.na(.)))) %>%
    
    gather(field, value, -set, -Study) %>%
    mutate(calc  = gsub(".*_", "", field),
           field = gsub("(.*)_.*$", "\\1", field)) %>%
    ungroup()
  
}

bind_rows(lapply(list(ia10.wes, ia9.wes, u1313), extract)) %>%
  mutate(c = paste(calc, Study, sep = "_")) %>%
  mutate(r = paste(field, set, sep = "_")) %>%
  select(c, r, value) %>%
  spread(key = c, value = value) %>%
  DT::datatable()
```
