---
title: "compare cluster constituents"
author: "Dan Rozelle"
date: "April 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("curation_scripts.R")
```

 < 2017-04-07_subset_for_clustering.R>
 in order to facilitate ideal clustering input I've been asked to generate
 a subset of patient-level data that includes only patients with:
 
>    Clinical outcome data (D_PFS and D_OS)
>    SNP
>    CNV
>    CYTO ( Translocations )
>    RNA  ( Normalized RNA-Seq trascript counts)
   
 Since I now have these data as individual patient-level summaries for nd.tumor
 data I can simply merge these tables together and retain only intersect rows.
 

```{r}
# import all of the master curated tables for annotating the c800 set
system(paste('aws s3 cp',
             file.path(s3, "ClinicalData/ProcessedData/Master/"),
             local,
             '--recursive', sep = " "))

# import individual cluster files
files <- list.files(local, full.names = T)
# remove unnecessary tables before import
files <- grep("curated*",files,value = T)

master        <- lapply(files, fread)
names(master) <- gsub("curated_([a-z]+)\\.txt", "\\1", tolower(basename(files)))
names(master)
# metadata master is a per-file and contains all files we are tracking, 
# including excluded and invalid samples.
nrow(master[['metadata']])

###
# import the 580 cluster patients I previously filtered
system(paste('aws s3 cp',
             file.path(s3, "ClinicalData/ProcessedData/Cluster/"),
             local,
             '--recursive --exclude "per.patient.all*"', 
             sep = " "))

# import individual cluster files
files <- list.files(local, full.names = T)
# remove unnecessary tables before import
files <- grep("clinical|cnv|rnaseq|snv|translocation|meta",files,value = T)

c579        <- lapply(files, fread)
names(c579) <- gsub(".*patient\\.([a-z]+)\\..*", "\\1", tolower(basename(files)))
names(c579)
# add a c579 designator
c579[['metadata']][,c579 := 1]
nrow(c579[['metadata']])

```


On Apr 7, 2017, at 4:04 PM, Wardell, Christopher <CPWardell@uams.edu> wrote:

> Thanks for the data.  I?ve been looking at it and realized that the so-called unified dataset that we?re working on isn?t the same as your 594 samples. 
>  
> Can we work out where the differences are?
>  
> I?ve attached a spread sheet showing how we split our data up;
>  
> Start with 1313 WES samples
> Keep only samples with copy number data (the ?CopyNumber.Pass? column), which is 1106 samples
> We found that patients aged 75 or older perform poorly, so removed them: 916 samples
> Required ISS stage data: 831 samples
> Survival data required: 800 samples
>  
> There is a column called ?TRAINTEST? which tells you which group each sample belongs to.  There will be 600 training samples, 200 test samples and the rest are > removed (there may be some NA values in there).
>  
> Can you tell me how you got to the 594 samples?  I guess we might need to start exchanging knitr documents to make this really exact.
>

```{r}
traintest <- GetS3Table(file.path(s3, "ClinicalData/ProcessedData/Cluster800", 
                                  "2017-04-07_TrainTest_from_ChrisWardell.txt")) %>%
  filter(TRAINTEST != "0") %>% mutate(c800 = 1)

nrow(traintest)
```

```{r}
# compare total overlap by patient identifier
venn::venn(list(c579 = c579[['metadata']]$Patient, c800 = traintest$Patient), cexil = 1.8, cexsn = 1.5)

df <- merge(select(c579[['metadata']],Patient, c579 ),
            select(traintest,       Patient, c800 ),
            by = "Patient", all = T)

classifiers <- master[['metadata']] %>%
  left_join(master[['clinical']] %>% select(-Study), by = "Patient")%>%
  group_by(Patient) %>%
  summarize(
    study       = unique(Study[!is.na(Study)]),
    excluded.patient = all(Excluded_Flag == 1),
    has.nd      = any(Disease_Status == "ND"),
    has.tumor   = any(Sample_Type == "NotNormal"),
    over.75     = any(D_Age >= 75),
    has.D_PFS   = any( !is.na(D_PFS)),
    has.D_OS    = any( !is.na(D_OS) ),
    has.D_ISS   = any( !is.na(D_ISS)))



has.cnv  <- master[['cnv']][,c("Patient", "File_Name")] %>% 
  rename(cnv.file = File_Name) %>% setkey(Patient)%>%
  local_collapse_dt(column.names = "Patient")
has.snv  <- master[['cnv']][,c("Patient", "File_Name")] %>% 
  rename(snv.file = File_Name) %>% setkey(Patient)%>%
  local_collapse_dt(column.names = "Patient")
has.rna  <- master[['rnaseq']][,c("Patient", "File_Name")] %>% 
  rename(rnaseq.file = File_Name) %>% setkey(Patient)%>%
  local_collapse_dt(column.names = "Patient")
has.trsl <- master[['translocations']][,c("Patient", "File_Name")] %>% 
  rename(translocation.file = File_Name) %>% setkey(Patient) %>%
  local_collapse_dt(column.names = "Patient")

merge_all <- function(dt1, dt2){merge(dt1, dt2,  all.x = TRUE)}
out <- Reduce(merge_all, list(df, classifiers, has.cnv, has.snv, has.trsl, has.rna)) %>%
  mutate(has.sample = TRUE,
         has.cnv = !is.na(cnv.file),
         has.snv = !is.na(snv.file),
         has.rna = !is.na(rnaseq.file),
         has.trs = !is.na(translocation.file),
         membership = case_when(
           is.na(.$c579) &   .$c800 == 1 ~ "c800",
             .$c579 == 1 & is.na(.$c800) ~ "c579",
             .$c579 == 1 & .$c800 == 1   ~ "both",
            
          
                                   TRUE ~ as.character(NA))
         ) 
# proportion of patients with a certain data type, split into three groups
out %>% group_by(membership) %>%  summarise_if(is.logical, mean, na.rm = T) %>% as.data.frame()
# count of patients with a certain data type, split into three groups
out %>% group_by(membership) %>%  summarise_if(is.logical, sum, na.rm = T) %>% as.data.frame()

# proportion of patients from c579 group
out %>% group_by(c579) %>%  summarise_if(is.logical, mean, na.rm = T) %>% filter( !is.na(c579)) %>% as.data.frame()
# count of patients from c579 group
out %>% group_by(c579) %>%  summarise_if(is.logical, sum, na.rm = T) %>% filter( !is.na(c579)) %>% as.data.frame()

# proportion of patients from c800 group
out %>% group_by(c800) %>%  summarise_if(is.logical, mean, na.rm = T) %>% filter( !is.na(c800)) %>% as.data.frame()
# count of patients from c800 group
out %>% group_by(c800) %>%  summarise_if(is.logical, sum, na.rm = T) %>% filter( !is.na(c800)) %>% as.data.frame()

```

```{r}
timestamp()
sessionInfo()
```