---
title: "MMRF sample flagging"
author: "Dan Rozelle"
date: "December 29, 2016"
output:
  html_document: default
  
---
<style> 
table { 
    font-size: 70%; 
    border-spacing: 0px;
    border-collapse: collapse;
} 
</style>



```{r, echo=F}
source("curation_scripts.R")
source("qc_and_summary.R")
s3 <- "s3://celgene.rnd.combio.mmgp.external"
itg <- "ClinicalData/ProcessedData/Integrated"
per.patient <- GetS3Table(file.path(s3, itg, "PER-PATIENT_clinical.txt"))
per.file <- GetS3Table(file.path(s3, itg, "PER-FILE_clinical_cyto.txt"))
```

#### SRR files in the WGS directory that correspond to existing WES files.
```{r}
knitr::kable(per.file[grepl("; ", per.file$File_Name_Actual),c("Sample_Name", "File_Name_Actual", "Sequencing_Type")])
```

#### Excluded files that we have 
```{r}
knitr::kable(per.file[(per.file$Excluded_Flag == 1 & !is.na(per.file$Excluded_Flag) & 
            per.file$File_Name_Actual != "" & !is.na(per.file$File_Name_Actual)),
         c("Sample_Name", "File_Path" ,  "Excluded_Specify")])
```

#### Files from IA9 SeqQC that we don't have
```{r}
df <- per.file[((per.file$Excluded_Flag == 0 | is.na(per.file$Excluded_Flag)) & 
           is.na(per.file$File_Path)),
         c("Sample_Name", "File_Path" ,  "Excluded_Specify")]
print("#none")
```

#### MMRF patients missing all clinical data
```{r}
valid.patients <- per.patient[
  apply(!is.na(per.patient[,grep("D_Gender", names(per.patient)):grep("^D_Best_Response$", names(per.patient))]), MARGIN = 1, any),"Patient"]
knitr::kable(per.file[!(per.file$Patient %in% valid.patients) & per.file$Study == "MMRF",c("Sample_Name", "File_Name_Actual", "Sequencing_Type")])
```

#### count file types we have for all datasets
```{r}
gplots::venn(list(
  `ND`=per.patient[per.patient$INV_Has.ND.sample == 1,"Patient"],
  `R`=per.patient[per.patient$INV_Has.R.sample == 1,"Patient"],
  `WES`=per.patient[per.patient$INV_Has.WES == 1,"Patient"],
  `WGS`=per.patient[per.patient$INV_Has.WGS == 1,"Patient"],
  `RNA-Seq`=per.patient[per.patient$INV_Has.RNASeq == 1,"Patient"]
))
```

#### count file types we have for MMRF
```{r}
dataset <- "MMRF"
gplots::venn(list(
  `ND`=per.patient[per.patient$INV_Has.ND.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `R`=per.patient[per.patient$INV_Has.R.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WES`=per.patient[per.patient$INV_Has.WES == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WGS`=per.patient[per.patient$INV_Has.WGS == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `RNA-Seq`=per.patient[per.patient$INV_Has.RNASeq == 1 & 
                     per.patient$Study == dataset,"Patient"]
))
```

#### count file types we have for DFCI
```{r}
dataset <- "DFCI"
gplots::venn(list(
  `ND`=per.patient[per.patient$INV_Has.ND.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `R`=per.patient[per.patient$INV_Has.R.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WES`=per.patient[per.patient$INV_Has.WES == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WGS`=per.patient[per.patient$INV_Has.WGS == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `RNA-Seq`=per.patient[per.patient$INV_Has.RNASeq == 1 & 
                     per.patient$Study == dataset,"Patient"]
))
```

#### count file types we have for UAMS
```{r}
dataset <- "UAMS"
gplots::venn(list(
  `ND`=per.patient[per.patient$INV_Has.ND.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `R`=per.patient[per.patient$INV_Has.R.sample == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WES`=per.patient[per.patient$INV_Has.WES == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `WGS`=per.patient[per.patient$INV_Has.WGS == 1 & 
                     per.patient$Study == dataset,"Patient"],
  `RNA-Seq`=per.patient[per.patient$INV_Has.RNASeq == 1 & 
                     per.patient$Study == dataset,"Patient"]
))
```


#### count file types we have for New Diagnosis MMRF
```{r}

gplots::venn(list(
  `WES`=per.patient[per.patient$INV_Has.WES == 1 & 
                     per.patient$Study == "MMRF" & per.patient$INV_Has.ND.sample == 1,"Patient"],
  `WGS`=per.patient[per.patient$INV_Has.WGS == 1 & 
                     per.patient$Study == "MMRF" & per.patient$INV_Has.ND.sample == 1,"Patient"],
  `RNA-Seq`=per.patient[per.patient$INV_Has.RNASeq == 1 & 
                     per.patient$Study == "MMRF" & per.patient$INV_Has.ND.sample == 1,"Patient"]
))
```

```{r}
get_inventory_counts(per.patient)
```