---
title: "SAS table export for previous ia9 data"
author: "Dan Rozelle"
date: "March 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../curation_scripts.R")
```

We would like to a side-by-side analysis comparison of IA9 and IA10 by Biostats. 
Since a number of significant changes to Disease_Status and PFS/OS were made to 
the integrated dataset after update to MMRF_IA10, we now must re-make the changes
before export to sas format. To facilitate this I've rerun the <curate_IA9.R> which 
was revised to exactly mirror the IA10 curation steps. I then ran a modified 
<mgp_clinical_aggregation.R> script to aggregate just the MMRF_IA9 and joint data 
files. This aggregation resultsed in the below files, which we will now use to 
create a unified table version, replace the MMRF rows in the current unified table,
and export this new version to sas.

- archive/per.file.clinical.nd.tumor_IA9_2017-03-23.txt
- archive/per.patient.clinical.nd.tumor_IA9_2017-03-23.txt

```{r}

integrated         <- "ClinicalData/ProcessedData/Integrated"

per.patient.mmrf9  <- GetS3Table(file.path(s3, integrated, "archive/per.patient.clinical.nd.tumor_IA9_2017-03-23.txt"))
per.file.mmrf9     <- GetS3Table(file.path(s3, integrated, "archive/per.file.clinical.nd.tumor_IA9_2017-03-23.txt"))


per.patient <- GetS3Table(file.path(s3, "ClinicalData/ProcessedData/Integrated/per.patient.clinical.nd.tumor.txt")) %>%
  filter( Study != "MMRF")
per.file    <- GetS3Table(file.path(s3, "ClinicalData/ProcessedData/Integrated/per.file.clinical.nd.tumor.txt")) %>%
  filter( Study != "MMRF") 

per.patient <-  bind_rows( list(per.patient, per.patient.mmrf9))
per.file    <-  bind_rows( list(per.file, per.file.mmrf9))


# make a unified table (file and patient variables) for nd.tumor data
unified.clinical.nd.tumor <- per.file %>%
  group_by(Study, Patient) %>%
  summarise_all(.funs = funs(Simplify(.))) %>%
  ungroup() %>%
  select(Patient, Study_Phase, Visit_Name, Sample_Name, Sample_Type, Sample_Type_Flag, Sequencing_Type, Disease_Status, Tissue_Type:CYTO_t.14.20._CONSENSUS) %>%
  full_join(per.patient, ., by = "Patient") %>%
  select(-c(starts_with("INV"))) %>%
  filter(Disease_Type == "MM" | is.na(Disease_Type))

PutS3Table(unified.clinical.nd.tumor, 
           file.path(s3, integrated, "archive/unified.clinical.nd.tumor_IA9_2017-03-23.txt"))
```


```{r}
# this has been adjusted to maintain a very specific export format, edit with care
# 
# It attempts to retain similarity in variable names and types to <SAS.TEMPLATE_2016-11-23.sas>
#
previous_columns <- scan("previous_columns.txt", what = character())

df    <- GetS3Table(file.path(s3, integrated, "archive/unified.clinical.nd.tumor_IA9_2017-03-23.txt"), check.names = F)
dict  <- GetS3Table(file.path(s3, integrated, "mgp_dictionary.xlsx"))

# sas column names are very restrictive, and automatically edited if nonconformant
# 32 char limit only symbol allowed is "_"
# export to sas automatically replaces each symbol with "_", truncates to 32 but has
# strange truncation rules (first lower case letters and then trailing upper case letters?)

# clean table names and dictionary names
names(df)  <- CleanColumnNamesForSAS(names(df))
dict$names <- CleanColumnNamesForSAS(dict$names)

# Compare with previous export and add back columns that have no info now but 
# might will in future analyses
p <- "CYTO|FLO|MISC|History"
df[,grep(p, setdiff(previous_columns, names(df)), value = T)] <-  NA

# get a column with type definitions
types      <- dict[  match(names(df), dict$names), "class"]
if(any( is.na(types)) ) warning(paste("Column(s):\"", names(df)[is.na(types)], "\" are not defined class in dict", sep = " "))

# coerce each variable
df <- df %>%
  # convert to appropriate variable type
  mutate_if(types == "numeric",   as.numeric)   %>%
  mutate_if(types == "factor",   as.factor)   %>%
  mutate_if(types == "character" | types == "date", as.character) %>%
  
  # leave NA values explicit and they will be suppressed in export
  mutate_if(types == "character", funs( gsub("^NA$", "", .) ))  %>%
  mutate_if(types == "character", funs( ifelse(is.na(.),"", .) )  ) %>%
  
  # remove all INV counting columns
  select(-c(starts_with("INV"))) %>%
  
  # remove new variables not required for analysis
  select(-c(Disease_Type)) %>%
  select(-ends_with("Date"))

# sort columns in dictionary order
tmp <- df[,dict$names[dict$names %in% names(df)]]
if( all(dim(tmp) == dim(df)) ){df <- tmp
}else{ stop("sorted columns didn't retain the same dimensions")}

# export as SAS format
name <- "unified.nd.tumor"
root <- paste0(name, "_IA9_", d)
local.data.path <- file.path(local, paste0(root,".txt"))
local.code.path <- file.path(local, paste0(root,".sas"))

foreign::write.foreign(df,
                       datafile = local.data.path,
                       codefile = local.code.path,
                       package="SAS")

# edit sas code table such that empty columns retain character length = 1
system( paste('sed -i "s/\\$ 0$/\\$ 1/" ', local.code.path, sep = " "))


# new columns
setdiff(names(df), previous_columns)
# lost columns
setdiff(previous_columns, names(df))

```

```{bash}
cat /tmp/curation/*sas
```

```{r}
# write to s3
# system(paste("aws s3 cp",
#              local.data.path,
#              file.path(s3, integrated, "sas/archive", paste0(root,".txt")),
#              "--sse", sep = " "))
# system(paste("aws s3 cp",
#              local.code.path,
#              file.path(s3, integrated, "sas/archive", paste0(root,".sas")),
#              "--sse", sep = " "))
```

