---
title: "MGP Translocation Consensus QC"
author: "Dan Rozelle, PhD"
date: "January 5, 2017"
output:
html_document: default

---
<style>
table {
font-size: 70%;
border-spacing: 0px;
border-collapse: collapse;
}
.table{
width: 40%;
}
</style>



```{r, echo=F}
source("curation_scripts.R")
source("qc_and_summary.R")
library(printr)

s3 <- "s3://celgene.rnd.combio.mmgp.external"
itg <- "ClinicalData/ProcessedData/Integrated"
per.patient <- GetS3Table(file.path(s3, itg, "PER-PATIENT_clinical.txt"))
per.file <- GetS3Table(file.path(s3, itg, "PER-FILE_clinical_cyto.txt"))

call.log <- read.delim("/tmp/cyto_consensus.log", stringsAsFactors = F)
```

The cytogenetic_consensus_calling script performs 3 sequential functions using results reported directly from dataset sources (FISH/cytogenetic calls)
and molecular calls we've performed from various techniques (MANTA, ControlFreec). 

1. Call consensus translocations using multiple techniques (FISH or MANTA). If longitudinal samples (ND, R, R2...) are not consistent for an individual translocation (t(4;14) ND=1, R=0) then a consensus is only called if the preferred technique is consistent

- t(4;14) | ND=1, R=1 by FISH | ND=NA, R=NA by MANTA | called as ND=1, R=1
- t(4;14) | ND=1, R=0 by FISH | ND=NA, R=NA by MANTA | called as ND=NA, R=NA
- t(4;14) | ND=1, R=0 by FISH | ND=0, R=0   by MANTA | called as ND=0, R=0

2. Calls the CYTO_Translocation_Consensus field by determining if a single t14 consensus translocation has been called for all samples (split by tumor or normal)

- t(4;14)=0;t(6;14)=0;t(11;14)=1;t(14;16)=0 | called as "11" 
- t(4;14)=0;t(6;14)=0;t(11;14)=1;t(14;16)=1 | called as "NA" 
- t(4;14)=0;t(6;14)=0;t(11;14)=0;t(14;16)=0 | called as ""

3. Similar to step 1, but for non-exclusive deletions and amplifications.

- amp(1q) | ND=0, R=1 by FISH | ND=NA, R=NA by MANTA | called as ND=0, R=1
- amp(1q) | ND=0, R=1 by FISH | ND=1,  R=NA by MANTA | called as ND=1, R=1

During the consensus calling run, each decision is logged for assessment later. Decisions are **all** if all techniques for a sample show the same result (or there is only one technique), **manta** if they are conflicting and we take the manta result as true, **no technique** if we have no results for the sample, and **ERROR** if longitudinal samples within the preferred/only method are inconsistent. 
```{r}
# count the total number of translocations that 
as.data.frame(table(call.log$decision))
```

As a side note, I also wanted to confirm that **CD138 PB** samples should be considered tumor samples with the same SV profile as **CD138 BM** samples?
```{r}
per.file[per.file$Patient == "MMRF_2531", c("Sample_Name", "Sequencing_Type", "Sample_Type", "Disease_Status", "Cell_Type", "Tissue_Type", grep("t.4.14", names(per.file), value = T) )]
```

Initially we only have 1 ERROR for the `r nrow(call.log)` translocation calls...not too bad ;) Lets inspect this error on the call.log and with more info on the per.file table. Looks like MMRF called the ndMM and relapse samples differently for t(11;14) by FISH, the translocation consensus calls for this are correctly left blank until we have manta results.
```{r, echo=F}
# count the total number of translocations that 
error.patient <- call.log[call.log$decision == "ERROR","Patient"]
error.trsl <- call.log[call.log$decision == "ERROR","Translocation"]

call.log[call.log$decision == "ERROR",c(1:3,5:7)]
per.file[per.file$Patient == error.patient, 
         c("Sample_Name_Tissue_Type", "Sequencing_Type", 
           grep("t.11|CYTO_Translocation_Consensus", names(per.file), value = T) )]

```

Looking more generally at translocation calls that were conflicting between techniques, but we had a preferred method (manta). In general it appears that MANTA is a more conservative translocation calling method compared to the clinical FISH results. 
```{r}
as.data.frame(table(call.log[call.log$conflicting_technique_results == TRUE,"raw_results"]))

```

The next step in translocation calling seeks to identify a single chr.14 translocation has been called for all samples (split by tumor or normal), and where >1 exclusive translocation is observed an ERROR2 is marked and should be inspected manually.
```{r, echo = F}
# subset for error samples and only consensus columns
df <- per.file[per.file$CYTO_Translocation_Consensus == "ERROR2", 
               c("Patient", "Sample_Name_Tissue_Type", "Study", names(per.file)[grepl("^CYTO_(t.*)_CONSENSUS", names(per.file))]) ]

error.patients <- unique(df$Patient)
names(df) <- gsub("CYTO_(t.[0-9]+.[0-9]+)._CONSENSUS", "\\1", names(df))
df <- df[!duplicated(df$Sample_Name_Tissue_Type),]
samples <- df$Sample_Name_Tissue_Type
df <- df[,grep("t.4.14", names(df)):ncol(df)]

trsl <- gsub("t.", "", names(df))
trsl <- gsub("14.|.14", "", trsl)

df <- data.frame(sample = samples,
                 flagged.translocations = unlist(apply(df, 1, function(x){ 
                   x[is.na(x)] <- "0"
                   x <- ifelse(x=="1",TRUE,FALSE)
                   paste(trsl[x], collapse = "; ")
                 }))
)
df

```

Print out more detail for which techniques were used to determine these conflicted calls.
```{r, echo=F}
for(p in error.patients){
  print(call.log[call.log$Patient == p & call.log$type_flag == "1" & !is.na(call.log$result) , 
                 c("Patient", "Translocation", "raw_results", "result")])
cat("\n")
  }

```